\documentclass[UTF8]{article}
%\usepackage{CTEX}
\title{Dovuq Dictionary}
\author{Dovuq}
\date{2020}
\newcommand{\flash}{$\sim$}
\begin{document}
    \setcounter{section}{-1}
    \setcounter{tocdepth}{1}
    \maketitle
    \newpage
    \tableofcontents
    \newpage
    \section{Tips}
    \paragraph{}
    Verbs has different tenses. There are Normeno, Fixano, Pastino, Omegano, and Futuro. The verb will write in Normeno. And other tenses will write after it. For example: sieque (siequan, sieque, sieque, siequ) Some verbs doesn't have some tenses. They will be written /
    \paragraph{}
    Noun's plural: usually -(e)s
    \paragraph{}
    Adjective's comparative: usually -ji
    \paragraph{}
    Adjective's superlative: usually -jest
    \newpage \section{A}
    \subsection{a/an}
    \paragraph{} art. a/an 
    \subsection{afta}
    \paragraph{} prep. after 
    \subsection{also}
    \paragraph{} adv. also, too, either 
    \subsection{an}
    \paragraph{} see "a" 
    \subsection{ani}
    \paragraph{} adj. any, some 
    \subsection{anis}
    \paragraph{} pron. anything, something, anybody, somebody
    \subsection{apot}
    \paragraph{} prep. up to
    \newpage \section{B}
    \subsection{bad}
    \paragraph{} adj. bad 
    \subsection{badli}
    \paragraph{} adv. badly, ill 
    \subsection{betali}
    \paragraph{} adv. again 
    \subsection{blud}
    \paragraph{} n. blood 
    \newpage \section{C}
    \subsection{can}
    \paragraph{} modal v. can 
    \subsection{cil}
    \paragraph{} num. 1,000 
    \subsection{cildis}
    \paragraph{} n. child 
    \subsection{coment (-tan, -tique, -tique, -tu)}
    \paragraph{} n. \& v. comment, commit 
    \subsection{corecto}
    \paragraph{} adj. correct
    \subsection{corectoli}
    \paragraph{} adv. correctly
    \subsection{crite (critan, criteque, criteque, critu)}
    \paragraph{} v. create
    \subsection{critiv}
    \paragraph{} adj. creative
    \newpage \section{D}
    \subsection{dafi (dafinan, dafi, dafi, dafiu)}
    \paragraph{} v. drop, or fall down (to the ground) 
    \subsection{dag}
    \paragraph{} n. day 
    \subsection{deci}
    \paragraph{} det. 1/10, 0.1 
    \subsection{demi}
    \paragraph{} det. 10, 10x 
    \subsection{des}
    \paragraph{} num. 10 
    \subsection{dez (/, dez, dez, /)}
    \paragraph{} v. die 
    \subsection{dictatit}
    \paragraph{} n. dictionary 
    \subsection{diel (dielan, dielique, dielique, dielu)}
    \paragraph{} v. dial, call 
    \subsection{Dovuq/Dovuque}
    \paragraph{} n. \& adj. Dovuq 
    \subsection{duo}
    \paragraph{} num. 2 
    \newpage \section{E}
    \subsection{e/ed}
    \paragraph{} conj. and 
    \subsection{ed}
    \paragraph{} see "e" 
    \subsection{els}
    \paragraph{} adv. else 
    \subsection{elz}
    \paragraph{} conj. because, but, although, etc. 
    \subsection{esli}
    \paragraph{} adv. usually 
    \newpage \section{F}
    \subsection{facio}
    \paragraph{} n. face 
    \subsection{fast}
    \paragraph{} adj. fast 
    \subsection{fastli}
    \paragraph{} adv. fast, quickly 
    \subsection{fish (fishan, fishe, fishique, fishu)}
    \paragraph{} n. fish 
    \paragraph{} v. wish, want (to) 
    \subsection{flond}
    \paragraph{} n. ground 
    \subsection{for}
    \paragraph{} adv. before, ago 
    \subsection{forgot (forgotan, forgot, forgot, forgetu)}
    \paragraph{} v. forget, forgive 
    \subsection{foto (fotonan, fotoque, fotoque, fotohu)}
    \paragraph{} n. photo 
    \paragraph{} v. photograph 
    \subsection{fqvrpe}
    \paragraph{} adv. extremely, or stronger than extremely 
    \newpage \section{G}
    \subsection{got (gotan, got, got, getu)}
    \paragraph{} v. get, have got 
    \subsection{gute}
    \paragraph{} adj. good 
    \subsection{guteli}
    \paragraph{} adv. well 
    \newpage \section{H}
    \subsection{habiq (habican, habique, habique, habiqu)}
    \paragraph{} n., v. \& int. bye, goodbye 
    \subsection{haroq (harocan, haroque, haroque, haroqu)}
    \paragraph{} n., v. \& int. hello, hi 
    \subsection{human}
    \paragraph{} n. human, man 
    \subsection{hundro}
    \paragraph{} num. 100 
    \newpage \section{I}
    \subsection{if}
    \paragraph{} conj. if 
    \subsection{im}
    \paragraph{} see is 
    \subsection{ir}
    \paragraph{} see is 
    \subsection{is (/, es/em/er, esque/emque/erque, isu)}
    \paragraph{} v. (also im/ir) be, am, is, are 
    \newpage \section{J}
    \subsection{jet}
    \paragraph{} n. \& int. yes 
    \newpage \section{L}
    \subsection{liter}
    \paragraph{} n. liter/litre 
    \newpage \section{M}
    \subsection{mi}
    \paragraph{} pron. I, me 
    \subsection{mig}
    \paragraph{} n. \& int. no 
    \subsection{mis}
    \paragraph{} pron. we, us 
    \subsection{misit}
    \paragraph{} pron. our, ours 
    \subsection{mit}
    \paragraph{} pron. my, mine 
    \subsection{miter}
    \paragraph{} n. meter/metre 
    \newpage \section{N}
    \subsection{nazin}
    \paragraph{} n. noun 
    \subsection{non}
    \paragraph{} num. 9 
    \newpage \section{O}
    \subsection{o/ot}
    \paragraph{} prep. to, of 
    \subsection{oct}
    \paragraph{} num. 8 
    \subsection{oquei}
    \paragraph{} int. OK, okay 
    \subsection{osie}
    \paragraph{} adv. of course 
    \subsection{ot}
    \paragraph{} see "o" 
    \newpage \section{P}
    \subsection{perlaps}
    \paragraph{} adv. perhaps, maybe 
    \subsection{pianti (piantinan, piantique, piantique, piantu)}
    \paragraph{} v. hit 
    \subsection{polises}
    \paragraph{} n. police 
    \newpage \section{Q}
    \subsection{quad}
    \paragraph{} num. 4 
    \subsection{quer}
    \paragraph{} pron. there, here 
    \subsection{querfor}
    \paragraph{} conj. therefore, so 
    \subsection{ques}
    \paragraph{} pron. this 
    \subsection{quet}
    \paragraph{} pron. that 
    \subsection{quint}
    \paragraph{} num. 5 
    \subsection{qus}
    \paragraph{} adv. thus
    \newpage \section{R}
    \subsection{repli (replinan, reple, repleque, replu)}
    \paragraph{} n. \& v. reply 
    \newpage \section{S}
    \subsection{sept}
    \paragraph{} num. 7 
    \subsection{seique (seiquan, seique, seique, seiqu)}
    \paragraph{} v. say, talk 
    \subsection{sex}
    \paragraph{} num. 6 
    \subsection{sieque (siequan, sieque, sieque, siequ)}
    \paragraph{} v. see 
    \subsection{spoca}
    \paragraph{} v. speak, similar as seique 
    \newpage \section{T}
    \subsection{tatle (tatelan, tatleque, tatleque, tatlu)}
    \paragraph{} n. \& v. title 
    \subsection{tato (tatonan, tatoique, tatoique, tatohu)}
    \paragraph{} n. \& v. time 
    \subsection{tatoit}
    \paragraph{} adv. on/in time 
    \subsection{tenci (tencan, tenced, tenced, tencu) c:/ts/}
    \paragraph{} v. go 
    \subsection{ti}
    \paragraph{} pron. he, him, she, her, it 
    \subsection{tinque (tinquan, tinque, tinque, tinqu)}
    \paragraph{} v. think
    \subsection{tis}
    \paragraph{} pron. they, them 
    \subsection{tisit}
    \paragraph{} pron. their, theirs 
    \subsection{tit}
    \paragraph{} pron. his, her, hers, its 
    \subsection{translatique (-quan, -que, -que, -qu)}
    \paragraph{} v. translate
    \subsection{translatiquit}
    \paragraph{} n. translation
    \subsection{tre}
    \paragraph{} num. 3 
    \newpage \section{U}
    \subsection{un}
    \paragraph{} num. 1 
    \subsection{uncorecto}
    \paragraph{} adj. incorrect, wrong
    \subsection{uncorectoli}
    \paragraph{} adv. incorrectly, wrong
    \newpage \section{V}
    \subsection{verbo}
    \paragraph{} n. verb 
    \subsection{veri}
    \paragraph{} adv. very 
    \subsection{vreti (vretinan, vrete, vreten, vretu)}
    \paragraph{} v. write 
    \newpage \section{Y}
    \subsection{yn}
    \paragraph{} pron. you, 1 person 
    \subsection{ynit}
    \paragraph{} pron. your, yours, 1 person 
    \subsection{yns}
    \paragraph{} pron. you, 2 persons or more 
    \subsection{ynsit}
    \paragraph{} pron. your, yours, 2 persons or more 
    \newpage \section{Z}
    \subsection{zaprise (zaprisnan, zapriseque, zapriseque, zapruse)}
    \paragraph{} n. \& v. surprise 
    \subsection{zau}
    \paragraph{} pron. how 
    \subsection{zei}
    \paragraph{} pron. why 
    \subsection{zeno}
    \paragraph{} pron. who 
    \subsection{zer}
    \paragraph{} pron. where 
    \subsection{zero}
    \paragraph{} num. 0
    \subsection{zes}
    \paragraph{} pron. what 
    \subsection{zeuf}
    \paragraph{} conj. \& adv. though
    \subsection{zien}
    \paragraph{} n. word 
    \subsection{zodique (zodicnan, zodique, zodique, zodiqu)}
    \paragraph{} v. shout (to/at) 
\end{document}